#Data Analysis on e-commerce website's performance
#Third-Party Platform: Poshmarks
#Data is authetic to personal e-commerce.

#Setting up directory for imports of data
```{r}
getwd()
setwd("/Users/StevenLu/Desktop")
getwd()
```

#Importing Data
#Data collected off PoshMark's website
```{r}
Data = read.csv("SalesData.csv", header = TRUE)
```

#Cleaning data/Remove insignificant variables
```{r}
Data = Data[-c(58:59),]
Data$SKU = NULL
Data$Cost.Price = NULL
Data$Other.Info = NULL
```

#Revaluing Women/Men to Dummy Variables(1,0)
```{r}
library(plyr)
Data$Department = revalue(Data$Department, c("Women"=1, "Men"=0))
head(Data$Department)
```

#Revaluing Y/N to Dummy Variables(1,0)
```{r}
Data$Bundle.Order. = revalue(Data$Bundle.Order., c("Y"=1,"N"=0))
Data$Offer.Order = revalue(Data$Offer.Order, c("Y"=1,"N"=0))
Data$NWT = revalue(Data$NWT, c("Y"=1,"N"=0))
```

#Manipulating Columns to remove $$
```{r}
Data$Net.Earnings = as.numeric(gsub("\\$", "", Data$Net.Earnings))
Data$Order.Price = as.numeric(gsub("\\$", "", Data$Order.Price))
Data$Seller.Shipping.Discount = as.numeric(gsub("\\$", "", Data$Seller.Shipping.Discount))
Data$Upgraded.Shipping.Label.Fee = as.numeric(gsub("\\$", "", Data$Upgraded.Shipping.Label.Fee))
Data$Sales.Tax..Paid.by.Buyer. = as.numeric(gsub("\\$", "", Data$Sales.Tax..Paid.by.Buyer.))
Data$Sales.Tax..Paid.by.Seller. = as.numeric(gsub("\\$", "", Data$Sales.Tax..Paid.by.Seller.))
```

#Creating a simple Linear Regression Model
```{r}
Linear.Model = lm(Net.Earnings ~ Order.Price, data = Data)
summary(Linear.Model)
```

#Package Installation
```{r}
install.packages("tidyverse")
install.packages("ggplot2")
```

#Creating Data Visualization of where my consumers are located
```{r}
library(ggplot2)
ggplot(data = Data, aes(y = Net.Earnings, x = Buyer.State))+
  geom_line(color = "Black", size = 1)
```
From the figure above, you can see that majority of my customers are in California and Washington. With this type of information, I can target consumers specifically based on seasons. 



